---
title: "Anime Alchemy"
author: "Zehaan Naik, Sneha Gupta, Sorbojit, Swapnonil"
format: html
editor: visual
---

## Introduction

The term "Anime" refers to all animated motion pictures that are produced in Japan. This is a booming industry with an ever-increasing audience and rising popularity. Naturally, this becomes an excellent opportunity for studios to make massive profits and an exciting field for one to study.

Anime Alchemy is a data visualization app that helps you analyze and compare the performance of various Anime series with several variables that define them. This application aims to help producers develop the best broadcasting and advertising model to ensure the success of their new program.

However, before diving into the application, we should first understand and explore the data set.

## Data

The data set we will be using for our analysis comprises the top 1000 Anime shows on the website [MyAnimeList](https://myanimelist.net/topanime.php). We shall talk more about scrapping the data set in a later section.

As mentioned, the data set comprises 1000 observations described using 38 variables. We can divide these variables broadly into two categories: numerical and categorical.

##### Numerical Variables:

These are the columns of our data set that have numerical values associated with them---for example, rating, number of likes, active viewers, etc.

These variables help us mathematically analyze the performance of several substrata of data points. Here is a brief description of all the columns that we have used in our analysis:

1.  [**Rating (Score):**]{.underline}

This is the average rating given to the show by everyone who rated the show. An important thing to note is that a high rating need not imply a more extensive audience size or popularity. The reason is that ten people can rate one show to be 9/10. However, another show might be rated by 100 people with a rating of 8.5. As a producer, you might favor the latter over the former.

2.  [**Number of Votes:**]{.underline}

This is the number of votes the show received on the website in a poll where users were asked about their top 10 favorite anime shows.

3.  [**Number of Favourites:**]{.underline}

This is the number of users who have marked a particular show as one of their favorites on the website.

4.  [**Number of Active Viewers:**]{.underline}

The number of people have watched over ten episodes of one particular show. Note that it is essential to distinguish between a viewer who has simply watched a single episode of a show and one who continuously watches the show. As a producer, we are primarily interested in the latter category predominantly.

5.  [**Number of Episodes:**]{.underline}

The number of episodes per season for a particular show.

6.  [**Duration Per Episode:**]{.underline}

The average duration per episode for the show.

(NOTE: Variables 5 and 6 are often used as grouping variables to analyze what range of episode number and duration sits well with a particular target audience.)

7.  [**Color Composition:**]{.underline}

We analyzed the posters for all the shows and studied the color composition of all the posters regarding their percentage RGB composition. We stored these values in separate columns to use as both grouping parameters and analysis parameters to explore various questions of possible co-relations between poster color composition and other parameters.

##### Categorical Variables:

These columns of our data set have non-numerical values such as names, seasons, origins, etc. We've used these values as grouping parameters to subset our data and observe various trends that emerge in such observations. Here is a brief description of all the groups that we have used:

1.  [**Source:**]{.underline}

Every anime has a source from which it is inspired. For example, we have "One Piece" inspired by Manga. Similarly, other sources may include games and comics; some might be original works.

2.  [**Genre:**]{.underline}

The genre of the show. It has categories like action, adventure, drama and comedy.

3.  [**Season of Premier:**]{.underline}

What season of the year was the anime premiered in? For example, it is a common understanding that shows meant for children perform better when released in summer. This is because many children are eager to consume TV content during their vacations. 

4.  [**Day of Telecast:**]{.underline}

The day of the week on which the show is telecasted.

5.  [**Target Demographic:**]{.underline}

The age section of the audience that the show is aimed at. For example, an anime series like "Shin-chan" is targeted toward a younger audience than compared to a series like "Full Metal Alchemist."

6.  [**Censorboard Rating:**]{.underline}

The age group that the censor board of Japan deems the show safe for.

## Obtaining Data

The data is scrapped from the website[ MyAnimeList](https://myanimelist.net/topanime.php).

The essential steps in our data preparation and cleaning are as follows:

-   The `rvest` and `tidyverse` libraries contain the scrapping functions, so they were first called at the beginning of writing the code. The `stringr` library came to our rescue as it helped remove any extra white spaces into a single white space.

-   With the help of running loops in `R`, we iterated to multiple sub-web pages of the website by changing the limits to an increment of 50. Multiple website links were stored in a vector named `links`, and additional essential elements were extracted.

-   To store the essential data elements required for data analysis, we had to name many dummy variables and iterate them over loops of the sub-web pages, thereby replacing their garbage value with the scrapped information from the website. Helpful functions such as `gsub`, `grepl`, `sapply`, `substring`, `paste`, `strsplit`, `str_squish`, and `trimws` made our data-scrapping task less challenging.

    1.  **`gsub`** function replaced all occurrences of patterns in character vectors with pre-specified replacements.

    2.  **`grepl`** function checked for the presence of patterns in character vectors. It returned a logical vector indicating patterns in each element.s

    3.  **`sapply`** function was applied to a function to each element of a list or vector and simplified the result.

    4.  **`substring`** function was used to extract or replace substrings from a character vector.

    5.  **`paste`** function was used to concatenate multiple strings into a single string.

    6.  **`strsplit`** function was used to split a character string into substrings based on a specified delimiter.

    7.  `str_squish` function removed leading, trailing, and repeated white space characters from a character vector.

    8.  **`trimws`** function was used to remove leading and trailing whitespaces (including spaces, tabs, and newlines) from character strings.

-   The data columns were converted to their correct types. For example, numeric real-valued data was converted to numeric type.

-   Many incorrect entries in columns related to theme, demography, and genre with the format "ExampleExample" were converted into "Example".

-   To calculate the airing duration between anime shows, `difftime` function was used. The ith element of paired columns was imputed in its function parameter with the difference unit in week rounded up to 2 decimal places.

-   We changed the value "None found, add some" to **NA** in the Licensor column.

Finally, with the help of the `data.frame` function, all the scrapped columns were bound horizontally and stored in an *anime_df* variable.

## Biases in Our Data

##### Non-Uniform Distribution of Observations

An important thing to note about our data set is that the number of observations we have for each subcategory is not uniform. For example, consider the \"Genres\" column. Here is a plot for the distribution of observation across the top 5 genres.

```{r}
#| echo: false
library(ggplot2)
MainData <- read.csv("Finaldata.csv")
genres <- as.data.frame(table(MainData$Genre))
genres <- genres[order(genres$Freq,decreasing = TRUE),]
genres <- genres[1:5,]
ggplot(genres, aes(x="", y=Freq, fill = Var1))+ 
  geom_bar(stat="identity", width=1, color = "white")+ 
  coord_polar("y", start=0)+
  theme_void()+
  labs(fill = "Genre")

```

We can observe that the "Action" genre contains the most data points, almost half of the entire data set. Hence, for any conclusion we make from the data based on the graphs where action comes out to be the most popular or most liked genre, we need to factor in this confounding variable of the number of observations. 

Hence, most of the analysis we present in our shiny app is on data subsetting to the user\'s needs. Also, we provide quantile analysis through box plots and base our conclusion on averages rather than the face value of data to mitigate the effect of such confounding variables.

We can further substantiate the argument by the following plot:

```{r}
#| echo: false
#| warning: false
ggplot(MainData, aes(x = Favorites/mean(Favorites), y = Score))+
  geom_point() + 
  xlim(1,5)+ 
  labs(x = "Normalised Number of Favourites", y = "Rating")
```

The plot clearly shows that the actual number of people who consider a particular anime to be their favorite has little correlation with the average rating that the show has on the website.

{{< pagebreak >}}

## Key Questions

Here are a few questions laid down by us looking at the dataset:

-   How do we ensure that our show does well?

    -   What season should you release the anime in?

    -   What day of the week should you broadcast the anime?

        -   During Weekends (Saturdays, Sundays)
        -   Just before the weekends (Fridays)
        -   Or during any other weekday

    -   How many episodes should there be per season?

    -   What should be the color composition of your poster?

        -   According to the Red, Green, Blue ( RGB % ).

    -   For a particular audience, what anime genre performs the best on an average?

    -   Which studio has the best performance average?

## Key Visualizations

```{r, echo=FALSE}

MainData <- read.csv("Finaldata.csv")

for(i in 1:1e3){
  ind = which.max(c(MainData$Percent.red[i],MainData$Percent.green[i],MainData$Percent.blue[i]))
  MainData$MainCol[i] <- c("Red","Green","Blue")[ind]
}
```

In our project we analysed our data and observed some visualization to know more about our data set. At first here comes our pie chart where we are categorising all the animes in different genres. Here is our pie chart

```{r, echo=FALSE}
library(ggplot2)
genres <- as.data.frame(table(MainData$Genre))
genres <- genres[order(genres$Freq,decreasing = TRUE),]
genres <- genres[1:5,]
ggplot(genres, aes(x="", y=Freq, fill = Var1))+ 
      geom_bar(stat="identity", width=1, color = "white")+ 
      coord_polar("y", start=0)+
      theme_void()+
      labs(fill = "Genre")
```

Some the key points that are specifing the data set in the pie chart are as follows;

\(a\) The split looks like this across various genres for the entire data.

\(b\) Action is the most prominent genre.

\(c\) The distribution of data across genres is different. Hence, the sampling must be done carefully, and the inferences must be drawn accordingly.

Now let us see another diagram. The following boxplots are comparing the average rating of anime grouped across various airing types.

```{r, echo=FALSE}
library(ggplot2)
ggplot(MainData,  mapping = aes(x = Score, y = Type))+
  geom_boxplot()
```


From the boxplots we can clearly see that the tv has more score than any other types such as movies or ONA etc.. The second most highest score accured by the animes is special type as the median is more than any other though for the movie types, the median is more less same the special type and the 3rd quartile is higher for movies.

Now let us concentrate in a comparative analysis between the acceptance of the animes according to the age groups. Here is a pie chart and some box plots, where the preferences of the genre for the 17+ audience.

```{r, echo=FALSE}
library(ggplot2)
genres <- as.data.frame(table(MainData$Genre[which(MainData$Source=="Manga" & MainData$Rating=="R - 17+ (violence & profanity)")]))
genres <- genres[order(genres$Freq,decreasing = TRUE),]
genres <- genres[1:5,]
ggplot(genres, aes(x="", y=Freq, fill = Var1))+ 
      geom_bar(stat="identity", width=1, color = "white")+ 
      coord_polar("y", start=0)+
      theme_void()+
      labs(fill = "Genre")
```


```{r, echo=FALSE}
library(ggplot2)
manga <- as.data.frame(MainData[which(MainData$Source=="Manga"), ])
ggplot(manga,  mapping = aes(x = Score, y = Genre))+
  geom_boxplot()
```

From the pie chart and the box plot, we can see that for the animes with manga as their source, the action genre is more popular than the rest. Comedy, fantasy, horror and supernatural genres appeals lesser to the 17+ audience. The score of the action genre is also dispersed than many of the other genres, though the drama genre is also dispersed.

Another pie chart is here where the preferences of the juvenile audience is shown.

```{r, echo=FALSE}
library(ggplot2)
genres <- MainData[which((MainData$Source=="Manga") & (MainData$Rating=="PG - Children")), ]
genres <- as.data.frame(table(genres$Genre[which(genres$Episode.Count<=50)]))
genres <- genres[order(genres$Freq,decreasing = TRUE),]
genres <- genres[1:5,]
ggplot(genres, aes(x="", y=Freq, fill = Var1))+ 
  geom_bar(stat="identity", width=1, color = "white")+ 
  coord_polar("y", start=0)+
  theme_void()+
  labs(fill = "Genre")
```

For the juvenile audience, the scenario changes. The comedy genre appeals the most, with a maximum episode count 50, which is pretty much evident.

## Conclusion

Concluding this project we were able to build an app which would help us to make different templates of the preferred combination of different characteristic variables (genre, broadcast day, studios, etc.. ), we used in our analysis.

We can notice that there is no specific combination of characterisitics which guarantees a hit anime but it depends on how the person who is making the Anime wants to make it.

our project focused on optimizing the success of an anime show, considering key factors such as the season of release, the day of the week, the number of episodes, and the most suitable genre for a specific target audience. We found that:

1.  Anime are most popular in winter and summer season.
2.  The choice of the day for releasing episodes can impact viewership.
3.  Action and adventure genre are more popular in 17+ audience while children are more interested in comedy genre.
4.  Dark colors dominate action and horror genre whereas no clear trend could be observed in other genres.

In essence, the success of an anime show is contingent on a meticulous blend of these factors. By strategically navigating the timing, episode count, and genre selection, we aim to optimize the viewing experience, ensuring the show not only captures the attention of the intended audience but also stands out in the competitive landscape. The culmination of these insights offers a comprehensive strategy to maximize the overall success and impact of the anime production.

## References

1.  [MyAnimeList](https://myanimelist.net/topanime.php)

2.  [Manga Genres](https://library.osu.edu/site/manga/manga-genres/)

3.  [Explanation of Manga Genres](https://beebom.com/anime-types-genres-explained/)

4.  [Wikipedia page for "Anime"](https://en.wikipedia.org/wiki/Anime)

5.  [A Beginners Guide to Manga](https://www.nypl.org/blog/2018/12/27/beginners-guide-manga)
